Using change scores

### 2022-03-12 text/22/baseline-covariate.Rmd
Kajor update to 14/history-of-r

---
title: "Mapping latitude and longitude"
author: "Steve Simon"
source: new
date: "2022-02-01"
category: 
- Blog post
tags:
- Analysis of covariance
- Incomplete page
output: html_document
---

>>>>

---
title: "Using change scores"
author: "Steve Simon"
source: new
date: "2022-02-01"
category: 
- Blog post
tags:
- Analysis of covariance
- Incomplete page
output: html_document
---
